---
title: "Team 16 Tier-3 single-model forecast"
subtitle: "Silicon Sample Benchmark"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                     fig.width = 10, fig.height = 6, dpi = 140)
library(dplyr)
library(readr)
library(tidyr)
library(ggplot2)
library(jsonlite)
metadata <- read_json("../../metadata.json", simplifyVector = TRUE)
models <- read_csv("../config/models.csv", show_col_types = FALSE)
forecasts <- read_csv("../outputs/derived/forecast_aggregation_long.csv", show_col_types = FALSE)
spread <- read_csv("../outputs/diagnostics/prompt_disagreement_by_cell.csv", show_col_types = FALSE)
outcomes <- read_csv("../inputs/tier3_outcomes.csv", show_col_types = FALSE)
interventions <- read_csv("../inputs/tier3_interventions.csv", show_col_types = FALSE)
model_label <- if (models$model_id[[1]] == "gemini-3.1-pro-preview") "Gemini 3.1 Pro Preview" else "Claude Opus 4.6"
model_fc <- filter(forecasts, aggregation_level == "model")
prompt_fc <- filter(forecasts, aggregation_level == "prompt")
```

This report documents the locked **`r model_label`** secondary submission from
team 16. It contains 208 average treatment effect (ATE) forecasts: one for each
of 16 interventions crossed with 13 outcomes.

> **What is an ATE?** Here, an ATE is the predicted average difference between
> people assigned to an intervention and people assigned to the neutral control.
> Positive and negative values indicate the direction of that difference; the
> units are the original units of each outcome.

# 1. Submitted method

The model received the intervention, control material, outcome definitions, and
native response scales. Two fixed, substantively equivalent prompts independently
requested all 13 signed ATEs for every intervention. The submitted value for each
cell is the median of those two prompt forecasts. There was no calibration,
shrinkage, clipping, or manual editing.

| Item | Value |
|:--|:--|
| Entry | `r metadata$entry` |
| Model | `r model_label` |
| Prompt variants | 2 |
| Completions per intervention-prompt | `r models$n_completions[[1]]` |
| Forecast cells | `r nrow(model_fc)` |
| Aggregation | Median across prompts |

# 2. Submitted forecast map

The heatmap is the complete submitted forecast. Because outcomes use different
native scales, color intensity should be compared primarily within an outcome
column rather than across columns.

```{r forecast-map}
ggplot(model_fc, aes(outcome, condition, fill = estimate)) +
  geom_tile(color = "white", linewidth = 0.15) +
  scale_fill_gradient2(low = "#2166AC", mid = "white", high = "#B2182B",
                       midpoint = 0, name = "ATE") +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_size = 11) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid = element_blank())
```

# 3. Forecast magnitude by outcome

This figure summarizes the distribution of absolute forecast magnitudes for each
outcome and orders outcomes by their median magnitude. It describes the model's
scale of predictions; it is not evidence of empirical accuracy.

```{r magnitude}
mag <- model_fc |>
  mutate(abs_ate = abs(estimate)) |>
  group_by(outcome) |>
  mutate(order_value = median(abs_ate)) |>
  ungroup() |>
  mutate(outcome = reorder(outcome, order_value))
ggplot(mag, aes(outcome, abs_ate)) +
  geom_boxplot(fill = "#5B8DB8", alpha = .75, outlier.alpha = .6) +
  coord_flip() +
  labs(x = NULL, y = "Absolute predicted ATE") +
  theme_minimal(base_size = 11)
```

# 4. Prompt robustness

Each point compares the two prompt formulations for one intervention-outcome
cell. Points close to the diagonal indicate that wording had little influence.

```{r prompt-robustness}
prompt_wide <- prompt_fc |>
  select(condition, outcome, prompt_id, estimate) |>
  pivot_wider(names_from = prompt_id, values_from = estimate)
prompt_names <- setdiff(names(prompt_wide), c("condition", "outcome"))
ggplot(prompt_wide, aes(x = .data[[prompt_names[[1]]]], y = .data[[prompt_names[[2]]]])) +
  geom_abline(slope = 1, intercept = 0, color = "grey60", linetype = 2) +
  geom_point(color = "#2C7FB8", alpha = .65, size = 2) +
  coord_equal() +
  labs(x = "Prompt 1 forecast", y = "Prompt 2 forecast") +
  theme_minimal(base_size = 11)
```

Pearson correlation across the 208 cells: **`r sprintf("%.3f", cor(prompt_wide[[prompt_names[[1]]]], prompt_wide[[prompt_names[[2]]]], method = "pearson"))`**.

## Cells most sensitive to prompt wording

The table lists the ten cells with the largest prompt range after dividing by
the width of that outcome's native scale. This makes sensitivity more comparable
across outcomes with different units.

```{r sensitive-cells}
spread |>
  arrange(desc(prompt_range_fraction)) |>
  select(condition, outcome, prompt_min, prompt_max, prompt_range_fraction) |>
  slice_head(n = 10) |>
  mutate(prompt_range_fraction = round(prompt_range_fraction, 3)) |>
  knitr::kable(col.names = c("Intervention", "Outcome", "Minimum", "Maximum",
                            "Range / scale width"))
```

# 5. Interpretation and reproducibility

This single-model entry is useful as a controlled comparison with the primary
three-family consensus: prompts and aggregation are held fixed while the model
contributor changes. Model-agreement statistics are not applicable within this
repository because it deliberately contains one submitted model.

The exact prompts, extracted benchmark inputs, archived structured responses,
aggregation code, locked prediction file, and provenance are deposited here.
Running scripts `03_build_submission.R` and `04_render_report.R` rebuilds the
derived forecast and this report without making model calls. Script
`02_run_forecasts.R` is retained for methodological transparency and defaults to
preview mode with model calls disabled.
